SMASH companion source code repository

### 2018-12-04 analysis/index.Rmd
wflow_publish(c("gaussian_signals.Rmd", "index.Rmd"))
Minor edits to home page.

2. [Estimating the variance function from Gaussian-distributed
data](gaussvarest.html).

>>>>

2. [Plots of the mean and variance functions used to simulate Gaussian data for the mean-estimation experiments.](gaussian_signals.html)

3. [Estimating the variance function from Gaussian-distributed
data.](gaussvarest.html)
